If the Null Fits, You Must Omit: Measurement Artifacts Undermine Group Polarization Replications

### 2025-10-30 GroupPolarizationStatmod/paper/ms.tex
fixed math problem

The measurement process with $N\to\infty$ participants is simulated by 
integrating the latent opinion distribution between ordinal bin thresholds, 
of which there are $B+1$, where $B$ is the number of opinion bins, with sequential
integer values $b \in \{0, B\}$. In the Moscovici and Zavalloni (1969)
example, the thresholds are \in
\{-\infty,-2.5,-1.5,\ldots,2.5,\infty\}$, with $B = 7$.
Bin $b$ is defined by its lower and upper continuous-valued thresholds, 
$\theta_{b-1}$ and
$\theta_{b}$, respectively. Thresholds are given by the following equations
(visualized as dotted lines in Figure~\ref{fig:distros}).
\begin{equation}
\theta_b = \begin{cases}
  -\infty         & \text{ if } b=0 \\
  \infty          & \text{ if } b=B \\
  \theta_{\text{Base}} + \frac{b}{2} & \text{ otherwise.}
\end{cases}
\end{equation}
\noindent
In the Moscovici and Zavalloni example, the base bin value is
$\theta_{\text{Base}} = -3$.
With thresholds defined, the frequency of ordinal measurment $b$ at time $t$ 
is (Figure~\ref{fig:distros})
\begin{equation}
  p(b;~\mu_t, \sigma_t, B) = \int_{\theta_{b-1}}^{\theta_b} p(\omega; \mu_t, \sigma_t)
  d\omega.
  \label{eq:ordinal-frequency}
\end{equation}

>>>>

The measurement process with $N\to\infty$ participants is simulated by 
integrating the latent opinion distribution between ordinal bin thresholds, 
of which there are $B+1$, where $B$ is the number of opinion bins, with sequential
integer values $b\{0, B\}$. In the Moscovici and Zavalloni (1969)
example, the thresholds are $\theta_b \in \{-\infty,-2.5,-1.5,\ldots,2.5,\infty\}$, with $B = 7$.
Bin $b$ is defined by its lower and upper continuous-valued thresholds, 
% $\theta_{b-1}$ and
$\theta_{b}$, respectively. Thresholds are given by the following equations
(visualized as dotted lines in Figure~\ref{fig:distros}).
\begin{equation}
\theta_b = \begin{cases}
  -\infty         & \text{ if } b=0 \\
  \infty          & \text{ if } b=B \\
  \theta_{\text{Base}} + \frac{b}{2} & \text{ otherwise.}
\end{cases}
\end{equation}
\noindent
In the Moscovici and Zavalloni example, the base bin value is
$\theta_{\text{Base}} = -3$.
With thresholds defined, the frequency of ordinal measurment $b$ at time $t$ 
is (Figure~\ref{fig:distros})
\begin{equation}
  p(b;~\mu_t, \sigma_t, B) = \int_{\theta_{b-1}}^{\theta_b} p(\omega; \mu_t, \sigma_t)
  d\omega.
  \label{eq:ordinal-frequency}
\end{equation}
